Multi-view 3D Aerosol Distribution Recovery

### 2013-07-28 article.tex
Added corrections by Vadim

The MC simulations use the same atmospheric grid described in
\cref{sec:single-scatt-model}. We use backward MC, i.e. photons are
traced from the detector, camera, to their source, the Sun, in a
direction determined by the camera model, i.e. hemispherical
camera. The quality of the simulations is proportional to the number
of photons. To create the \cref{fig:simulation-results1}b, \num{10000}
photons were emitted from each pixel. The distance travelled by the
photon till its first scattering is determined by sampling from the
transmittance distribution using the inverse transform sampling
(\cref{sec:theor-backgr}).  The CDF of the transmittance distribution
is given by,
\begin{equation}
  \label{eq:1}
  F=\int_{0}^{1}\exp(-\tau)\derivsym{\tau}=1-\exp(-\tau)
\end{equation}
Given a uniformly distributed random number $u$ a random transmittance
is given by
\begin{equation}
  \label{eq:2}
  t=F^{-1}(u)=-\ln(1-u)
\end{equation}
If the scattering occurs outside the atmospheric grid, the photon is
dropped. If not, the voxel in which the scattering occurs is
calculated.  The type of scattering, either by air molecule or aerosol
particle, is determined randomly according to their relative densities
in the voxel.  The new direction of the photon is determined by
inverse sampling the phase function of the scattering particle:
Rayleigh, \cref{eq:rayleighP}, or Henyey-Greenstein,
\cref{eq:aerosol_scatter}.  Local Estimation~\cite{marshak20053d} is
used for calculating the amount of light reaching the sun at each
scattering.  This process is repeated till the photon escapes the
atmosphere grid or it reaches a predetermined number of scatterings.

>>>>

The MC simulations use the same atmospheric grid described in
\cref{sec:single-scatt-model}. We use backward MC, i.e. photons are
traced from the detector, camera, to their source, the Sun, in a
direction determined by the camera model, i.e. hemispherical
camera. The quality of the simulations is proportional to the number
of photons. To create the \cref{fig:simulation-results1}b, \num{10000}
photons were emitted from each pixel. The distance travelled by the
photon till its first scattering is determined by sampling from the
transmittance distribution using the inverse transform sampling
(\cref{sec:theor-backgr}).  The CDF of the optical depth
(transmittance) distribution is given by,
\begin{equation}
  \label{eq:1}
  F=\int_{0}^{\tau}\exp(-\tau')\derivsym{\tau'}=1-\exp(-\tau)
\end{equation}
Given a uniformly distributed random number $u$ a random optical depth
is given by
\begin{equation}
  \label{eq:2}
  t=F^{-1}(u)=-\ln(1-u)
\end{equation}
The actual distance travelled by the photon is calculated by
accumulating the discrete optical depths of each voxel along the
photon's path till the target optical path, drawn by \cref{eq:2}, is
reached.  If the scattering occurs outside the atmospheric grid, the
photon is dropped. If not, the voxel in which the scattering occurs is
calculated.  The type of scattering, either by air molecule or aerosol
particle, is determined randomly according to their relative densities
in the voxel.  The new direction of the photon is determined by
inverse sampling the phase function of the scattering particle:
Rayleigh, \cref{eq:rayleighP}, or Henyey-Greenstein,
\cref{eq:aerosol_scatter}.  Local Estimation~\cite{marshak20053d} is
used for calculating the amount of light reaching the sun at each
scattering.  This process is repeated till the photon escapes the
atmosphere grid or it reaches a predetermined number of scatterings.
